Luminosity function of RGHJs

### 2015-11-16 luminosity.tex
flux distribution...??

\title{Luminosity function of RGHJs}
\author{Yuka Fujii\altaffilmark{1}}
\altaffiltext{1}{Institute of Astronomy, Madingley Road, University of Cambridge, Cambridge CB3 0HA, United Kingdom}

@@

%Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in our neighborhood of the Galaxy. 
In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$. 
Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
. Therefore, $\alpha_L \sim -3.1$.

Assume:
%%%
\begin{displaymath}
\frac{dn}{dL} = \left\{
\begin{array}{ll}
C L^{-\alpha } & (L_{\rm min} < L < L_{\rm max}) \\
0 & (\mbox{elsewhere})
\end{array}
\right.
\end{displaymath}
%%%
where $C $ is the proportional coefficient. 
%%%
\begin{equation}
\frac{d^2n}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr 
\end{equation}
%%%

The relationship between flux $F$ and Luminosity $L$ is:
%%%
\begin{equation}
F = \frac{L}{r^2}
\end{equation}
%%%
where $r$ is the distance to the target.

The number of the targets within distance $R$ which have flux at $F \sim F+dF$ is
%%%
\begin{eqnarray}
\frac{dn}{dF} dF &=& \int dr \int dL \; \Psi (L, r) \\
&=& \int _{F}^{F+dF} dF \int _0^{R} dr \; \Psi (F r^2, r)\; det(J) 
\end{eqnarray}
%%%
where
%%%
\begin{equation}
det(J) = \left| \PD{r}{r}\PD{L}{F} - \PD{r}{F}\PD{L}{r} \right| = r^2
\end{equation}
%%%

Therefore, 
%%%
\begin{eqnarray}
\frac{dn}{dF} dF &=& \left[ 4 \pi \int _0 ^{R} dr \; r^4 \Phi (F, r) \right] dF\\
\Phi (F, r) &=& \left\{
\begin{array}{ll}
C (F r^2)^{-\alpha } & (\sqrt{L_{\rm min}/F} < r < \sqrt{L_{\rm max}/F}) \\
0 & (\mbox{elsewhere})
\end{array}
\right. 
\end{eqnarray}
%%%

Thus,  
%%%
\begin{eqnarray}
&& \frac{dn}{dF} dF \\
&& = \left\{
\begin{array}{l}
0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{R^2} \right) \\
\\
\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha} \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{R^2} < F < \frac{L_{\rm max}}{R^2} \right) \\	
\\
\displaystyle \frac{4\pi C F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{F}} \right)^{5 - 2\alpha } \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{R^2} < F \right) 
\end{array}
\right. \\
%%%
&& = \left\{
\begin{array}{l}
0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{R^2} \right) \\
\\
\displaystyle \frac{4\pi C }{5 - 2\alpha} \left[ R^{5 - 2\alpha}F^{-\alpha } -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{R^2} < F < \frac{L_{\rm max}}{R^2} \right) \\	
\\
\displaystyle \frac{4\pi C F^{-2.5 }}{5 - 2\alpha} \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{R^2} < F \right) 
\end{array}
\right. 
\end{eqnarray}
%%%

>>>>

\title{Luminosity function of RGHJs}
\author{Yuka Fujii\altaffilmark{1}}
%\altaffiltext{1}{Institute of Astronomy, Madingley Road, University of Cambridge, Cambridge CB3 0HA, United Kingdom}

@@

%Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in our neighborhood of the Galaxy.

We consider the number density of observed flux from targets within the distance $R$. 
Luminosity and (observed) flux are denoted by $L$ and $F$, respectively. 
\vspace{1\baselineskip}

Let us denote the number density of evolved stars per unit volume by $n$ and assume that the luminosity function can be written as follows. 
%%%
\begin{equation}
\frac{dn}{dL} = \left\{
\begin{array}{ll}
C L^{-\alpha } & (L_{\rm min} < L < L_{\rm max}) \\
0 & (\mbox{elsewhere})
\end{array}
\right. 
\end{equation}
%%%
Here, $C $ is the proportional coefficient.

Then, let us denote the (expected) total number of evolved stars in a sphere of radius $R$ by $N$. Consider a spherical shell at radius $r$ ($r<R$) with thickness $dr$. The number of evolved stars in this spherical shell and with luminosity ranging from $L\sim L+dL$ is:
%%%
\begin{equation}
\frac{d^2N}{dL dr} dL dr = 4 \pi C L^{-\alpha } r^2 dL dr \equiv \Psi (L, r) dL dr \label{eq:d2N/dLdr}
\end{equation}
%%%

The relationship between flux $F$ and luminosity $L$ is, as usual,
%%%
\begin{equation}
F = \frac{L}{4\pi r^2} 
\end{equation}
%%%
where $r$ is the distance to the target.

Now, we want to get the number of targets with flux between $F$ and $F+dF$. 
To do so, we want to integrate equation (\ref{eq:d2N/dLdr}) over the parameter space $\mathcal{S}$ satisfying
%%%
\begin{equation}
F < \left( \frac{L}{4\pi r^2} \right) < F+dF 
\end{equation}
%%%
To do so, we change the set of variables from $\{ L,\,r \}$ to $\{ F,\,r \}$. 
Thus,
%%%
\begin{eqnarray}
\frac{dN}{dF} dF &=& \iint _{\mathcal{S}}  dr dL \;\; \Psi (L, r) \\
&=& \int _0^{R} dr \int _{F}^{F+dF} dF' \;\; \Psi (4\pi r^2F', r)\; det(J) 
\end{eqnarray}
%%%
where
%%%
\begin{equation}
det(J) = \left| \PD{r}{r}\PD{L}{F'} - \PD{r}{F'}\PD{L}{r} \right| = 4 \pi r^2
\end{equation}
%%%

Therefore, 
%%%
\begin{eqnarray}
\frac{dN}{dF} dF &=& \left[ \int _0 ^{R} dr \; \Phi (F, r) \right] dF\\
\Phi (F, r) &=& \left\{
\begin{array}{ll}
C' F^{-\alpha } r^{4-2\alpha} & (\sqrt{L_{\rm min}/4 \pi F} < r < \sqrt{L_{\rm max}/4 \pi F}) \\
0 & (\mbox{elsewhere})
\end{array}
\right. \\
C' &\equiv & C ( 4 \pi )^{2-\alpha }
\end{eqnarray}
%%%

Thus,  
%%%
\begin{eqnarray}
&& \frac{dN}{dF} dF \\
&& = \left\{
\begin{array}{l}
0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{4\pi R^2} \right) \\
\\
\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ R^{5 - 2\alpha} - \left( \sqrt{ \frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha} \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{4\pi R^2} < F < \frac{L_{\rm max}}{4\pi R^2} \right) \\	
\\
\displaystyle \frac{C' F^{-\alpha }}{5 - 2\alpha} \left[ \left( \sqrt{ \frac{L_{\rm max}}{4\pi F} } \right)^{5 - 2\alpha} - \left( \sqrt{\frac{L_{\rm min}}{4\pi F}} \right)^{5 - 2\alpha } \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{4\pi R^2} < F \right) 
\end{array}
\right. \\
%%%
&& = \left\{
\begin{array}{l}
0 \;\;\;\; \displaystyle \left( F < \frac{L_{\rm min}}{4\pi R^2} \right) \\
\\
\displaystyle \frac{C' }{5 - 2\alpha} \left[ R^{5 - 2\alpha}F^{-\alpha } -  L_{\rm min}^{2.5 - \alpha} F^{-2.5} \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\;  \displaystyle \left( \frac{L_{\rm min}}{4\pi R^2} < F < \frac{L_{\rm max}}{4\pi R^2} \right) \\	
\\
\displaystyle \frac{C' F^{-2.5 }}{5 - 2\alpha} \left[ L_{\rm max}^{2.5 - \alpha} - L_{\rm min}^{2.5 - \alpha}  \right] dF \\
\\
\;\;\;\;\;\;\;\;\;\;\;\;\;\; \displaystyle \left( \frac{L_{\rm max}}{4\pi R^2} < F \right) 
\end{array}
\right. 
\end{eqnarray}
%%%

\vspace{1\baselineskip}

For now, let us suppose
%%%
\begin{itemize}
\item range of luminosity of ``evolved stars'':\\$L_{\odot }-10,000 L_{\odot }$
\item $\Rightarrow$ minimum radio luminosity of ``RGHJs''\\%
$L_{\rm min} = 2,1\times 10^{11}/30 {\rm MHz} = 7000 {\rm W/Hz}$
\item $\Rightarrow $maximum radio luminosity of ``RGHJs'':\\$L_{\rm max} = 4.5\times 10^{13} {\rm W}$
\end{itemize}
%%%
We also assume $\alpha = -3.1$; see next subsection.

\subsection{Actual luminosity function (?)}

In order to estimate the luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
For a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{7/12} M_\star^{1/6} T_{\rm eff}^{8/3} (1+A/g_\star)^{2/3}$. 
Given that the dependences on $M_\star^{1/6}$ is relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{7/12}$. 
Observations of globular clusters indicates the luminosity function of red giants is $dn/dL_{\star } \sim L_{\star }^{-1.8}$ (Sandquist et al. (1996)) %\citep{sandquist1996}
. Therefore, $\alpha \sim -3.1$.
